---
title: "2019-02-22_Peltier_Weight"
author: "Nicolas May"
date: "2/25/2019"
output: 
  html_document:
    theme: sandstone
    highlight: zenburn
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load Requirements

## Load Useful Globals & Functions

```{r}
source("~/Desktop/config.R")
source("~/Desktop/helpers.R")
```

## Load Useful Packages

```{r}
library(dplyr)
library(stringr)
```


# Get Data

## Define Data Fields

```{r}
# Form Header fields
fields_u3_hd_raw <-
  c(
    "ptid"
    , "form_date"
  ) 
# Form B1 fields
fields_u3_b1_raw <-
  c(
    "weight"
  ) %>% 
  c(., paste0("fu_", .), paste0("tele_", .))

# Combine and collapse
fields_u3_raw <- 
  c(
    fields_u3_hd_raw
    , fields_u3_b1_raw
  )
fields_u3 <- fields_u3_raw %>% paste(collapse = ",")
```

## Retreive Data via REDCap API

```{r}
# JSON
json_u3 <- rc_api_get(uri    = REDCAP_API_URI,
                      token  = REDCAP_API_TOKEN_UDS3n,
                      fields = fields_u3)

# JSON => dataframe
df_u3 <- jsonlite::fromJSON(json_u3) 
```

# Process Data

## Clean Data

```{r}
df_u3_cln <- df_u3 %>% 
  # Empty strings ("") and "888" are `NA`s
  na_if("") %>% na_if("888") %>% 
  # deslect useless field(s)
  select(-redcap_event_name) %>% 
  # clean out missing `form_date`s
  filter(!is.na(form_date)) %>% 
  # clean out DDE records (--1, --2)
  filter(str_detect(ptid, "^UM\\d{8}$")) %>% 
  # coalesce `weight` fields
  coalesce_ift_cols() %>% 
  # keep only most recent visits
  get_visit_n(id_field = ptid, form_date, n = Inf)
```

## Mutate Data

Coerce `weight` fields to integer.

```{r}
df_u3_cln_mut <- df_u3_cln %>% 
  mutate(weight = as.integer(weight))
```


# Summarize Data

Of the most recent visits (n = `r nrow(df_u3_cln_mut)`), how many are missing `weight` (or `fu_weight`) values?

```{r}
df_u3_cln_mut %>% 
  filter(is.na(weight)) %>% 
  summarize(n = n())
```

The answer is `r df_u3_cln_mut %>% filter(is.na(weight)) %>% summarize(n = n())`.

What are the descriptives of the `weight` field, removing `NA`s.

```{r}
df_u3_cln_mut %>%
  filter(!is.na(weight)) %>% 
  summarize(n    = n(),
            Mean = mean(weight),
            SD   = sd(weight),
            Min  = min(weight),
            LQ   = quantile(weight, 0.25),
            Med  = median(weight),
            UQ   = quantile(weight, 0.75),
            Max  = max(weight)) %>% 
  knitr::kable(format = "html") %>% 
  kableExtra::kable_styling(
    bootstrap_options = c("striped", "hover", "condensed", "responsive")
  )
```




```{r echo=FALSE}
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
#  @##==---==##@##==---==##@    EXTRA  :  SPACE    @##==---==##@##==---==##@  #
#@##==---==##@   @##==---==##@    #==-- --==#    @##==---==##@   @##==---==##@#
##==---==##@   #   @##==---==##@    #==-==#    @##==---==##@   #   @##==---==##
#=---==##@    #=#    @##==---==##@    #=#    @##==---==##@    #=#    @##==---=#
#--==##@    #==-==#    @##==---==##@   #   @##==---==##@    #==-==#    @##==--#
#==##@    #==-- --==#    @##==---==##@   @##==---==##@    #==-- --==#    @##==#
###@    #==--  :  --==#    @##==---==##@##==---==##@    #==--  :  --==#    @###
```
